article title

### 2022-07-08 article.tex
Clean up preamble
Add acknowledgement
Add supporting information
Add citations, bibliography
Add bold, italics, underline

\usepackage{graphicx}
\graphicspath{{fot/}}
\usepackage[export]{adjustbox}
\usepackage[singlelinecheck=false,justification=justified]{caption}

@@

@@

\section{Work in progress}
\label{sec:work_in_progress}

\section{Graphics}
\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\section{Tables}
\label{sec:tables}

@@

\section{Mathematics}
\label{sec:mathematics}

@@

@@

\subsection{Almost done}
\label{sec:even_more_to_do}
Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

@@

lists

@@

>>>>

% this package has better control over images
\usepackage{graphicx}
\graphicspath{{fot/}}
\usepackage[export]{adjustbox}
\usepackage[singlelinecheck=false,justification=justified]{caption}

@@

% set references indent

@@

\section{Bold, italics, and underline}
\label{sec:bold_italics_underline}
Bold text is done with \textbackslash{textbf\{\textless text \textgreater\}} such as \textbf{bolded text}.

Italics text is done with \textbackslash{textit\{\textless text \textgreater\}} such as \textit{italics text}.

Underline text is done with \textbackslash{underline\{\textless text \textgreater\}} such as \underline{italics text}.

Bold and italics text is done with \textbackslash{textbf\{\textbackslash{textit\{\textless text \textgreater\}\}} such as \textbf{\textit{bolded text}}.

Some of the \textbf{greatest} \textit{discoveries} in \underline{science} were made by \textbf{\textit{accident}}.

\newpage
\section{Graphics}
\label{sec:graphics}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\newpage
\section{Tables}
\label{sec:tables}

@@

\newpage
\section{Mathematics}
\label{sec:mathematics}

@@

\newpage
\section{Citations}
\label{sec:citations}
The formatting of the bibliography is not quite what I wish. I will explore bibtex for this. For now, here is how to site articles, books, and online references.

Blah blah \cite{JD} and blah blah \cite{JS} and blah blah \cite{JT}.

@@

@@

@@

\section{Acknowledgement}
\label{sec:acknowledgement}

The author wishes to thank ...

\section{Supporting information}
\label{sec:supporting_information}

Add files, data, and other supporting information, and where it can be obtained.

\begin{thebibliography}{99}
\bibitem{JD} Doe, John. 2000. Title of book.
\bibitem{JS} Smith, John. 2013. \textit{Title of article}.
\bibitem{JT} Thomas, John. 2022. \textit{Online reference}.
\end{thebibliography}
